\documentclass[]{resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     LAST UPDATED DATE
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \lastupdated

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     TITLE NAME
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \namesection{Jitendra}{Singh}{\urlstyle{same}\href{mailto:jeet.mp3@gmail.com}{jeet.mp3@gmail.com} | +91-9990446178}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN ONE
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \begin{minipage}[t]{0.33\textwidth}

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     SKILLS
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

        \section{Skills}\label{sec:skills}
        \subsubsection{Core}
        \textbullet{} Algorithms and Data structures\\
        \subsubsection{Programming}
        \textbullet{} Java \textbullet{} Groovy\\
        \subsubsection{Frameworks}
        \textbullet{} Spring Framework \textbullet{} Spring Boot\\
        \textbullet{} Hibernate\\
        \subsubsection{Security}
        \textbullet{} Spring Security \textbullet{} OpenID Connect\\
        \textbullet{} OAuth2\\
        \subsubsection{Database}
        \textbullet{} MySQL \textbullet{} MongoDB\\
        \subsubsection{Cloud}
        \textbullet{} Azure \textbullet{} AWS\\
        \subsubsection{Build Tools}
        \textbullet{} Gradle \textbullet{} Maven\\
        \subsubsection{Testing Frameworks}
        \textbullet{} Junit \textbullet{} Mockito \textbullet{} Spock\\
        \subsubsection{Editors}
        \textbullet{} Idea IntelliJ \textbullet{} VIM \textbullet{} Eclipse\\
        \subsubsection{Operating System}
        \textbullet{} UN*X \textbullet{} Linux \textbullet{} Windows\\
        \subsubsection{BigData}
        \textbullet{} HDFS \textbullet{} Hive \textbullet{} Spark\\
        \subsubsection{Others}
        \textbullet{} Consul \textbullet{} GraphQL\\
        \sectionsep
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     LINKS
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

        \section{Links}\label{sec:links}
        Blog: \href{https://dev.to/jeetmp3}{\textbf{https://dev.to/jeetmp3}}\\
        Github: \href{https://github.com/jeetmp3}{\textbf{@jeetmp3}}\\
        LinkedIn: \href{https://www.linkedin.com/in/jitendra-bisht-a7a25845/}{\textbf{@jitendra-bisht-a7a25845}}\\
        Twitter: \href{https://twitter.com/JitendraBisht27}{\textbf{@JitendraBisht27}}\\
        \href{https://drive.google.com/file/d/1A-Ol0hMl7bzwiPwvkwAmhSSblKBC4NUc/view?usp=sharing}{more..}
        \sectionsep

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %
        %     COLUMN TWO
        %
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.66\textwidth}

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     EXPERIENCE
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

        \section{Experience}\label{sec:experience}
        \runsubsection{BNY Mellon}
        \descript{| Application Lead Developer}
        \location{Jul 2018 - Present | Pune, IN}
        \vspace{\topsep}
        \begin{tightemize}
            \item Backend developer
            \item Working with remote team and ensuring quality deliverables for the client.
            \item Worked on RBAC AuthZ framework to grant Role Based access.
        \end{tightemize}
        \sectionsep

        \runsubsection{Bharti Airtel}
        \descript{| Lead Engineer }
        \location{November 2017 – June 2018 | Gurugram, IN}
        %\vspace{\topsep}
        \begin{tightemize}
            \item Worked as Lead engineer on SIM Acquizition product.
        \end{tightemize}
        \sectionsep

        \runsubsection{TO THE NEW}
        \descript{| Associate Tech Lead - Technology }
        \location{May 2014 – November 2017 | Noida, IN}
        \begin{tightemize}
            \item Worked as fullstack developer.
            \item Managed team of 6 developer.
            \item Ensuring quality deliverables for the client.
        \end{tightemize}
        \sectionsep

        \runsubsection{Spice Digital Ltd.}
        \descript{| Software Engineer}
        \location{August 2012 – May 2014 | Noida, IN}
        \begin{tightemize}
            \item Worked on multiple internal products.
            \item Worked as fullstack developer.
        \end{tightemize}
        \sectionsep

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     Open Source
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

        \section{Open source}\label{sec:open-source}
        \vspace{\topsep}
        \begin{tightemize}
            \item \href{https://plugins.grails.org/plugin/jeetmp3/spring-session}{\textbf{Owner of} Spring-session grails plugin}.
            \item \textbf{Contribution to Spring Community}
                \begin{enumerate}
                    \item \small Jackson mixin classes added in \textbf{spring-security} core, cas and web modules.
                    \item Added a project sample in \textbf{spring-session} to demonstrate JSON based session
                    serialization in redis.
                \end{enumerate}
        \end{tightemize}
        \sectionsep

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     CERTIFICATIONS
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \section{Certifications}\label{sec:certifications}
        \vspace{\topsep}
        \begin{tightemize}
            \item \href{https://drive.google.com/file/d/0B3T07LM4mDj8SnFiOGl4LTZsaVk/view}{\textbf{MongoDB Certification for Java developer}}\\
            bit.ly/mongocertificate
            {\vspace{\topsep}}
            \item \href{https://www.edureka.co/my-certificate/eadaa90dfc3b7655d95d57f5413043f6}{\textbf{Big Data certification}}\\
            bit.ly/bigdata\_certificate
        \end{tightemize}
        \sectionsep

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     Education
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

        \section{Education}\label{sec:education}
        \subsection{Uttarakhand Technical University}\label{subsec:uttarakhand-technical-university}
        \descript{Masters in Computers Application}
        \location{May 2009 | Dehradun, IN | 2012}

        \subsection{Kumaun University Nainital}\label{subsec:kumaun-university-nainital}
        \descript{Bachelores in Computers Application}
        \location{May 2006 | Nainital, IN | 2009}

        \sectionsep

    \end{minipage}
\end{document}  \documentclass[]{article}
